### 2018-04-22 papers/synth/encoding.tex
parsing fixed

The missing information can be in any of these combinations parts of VTS. For example existence of some undiscovered edges or nodes, or insufficient knowledge about the presence of molecules in some part of the VTS (either on the node or on the edge). To cover most of the likely variations of this missing information we have encoded the following variants of VTS synthesis.
%
%
\begin{enumerate}[label=\Alph*]
\item  Add new edges to the given VTS to achieve graph stability, fusion and k connected. 
\item  Modify the flow of molecules on the nodes and on the edges.
  \begin{enumerate}
  	\item use available set of molecules.
    \item allow new molecule type to be added.     
  \end{enumerate}        
\item Learning meaningful activity function. 
  \begin{enumerate}
    \item kcnf: low depth circuit.
    \item Boolean gates: And, Or.
    \item Boolean gates with linear combination.  
  % - Function dependence with var occurring once.
\item  VTS repair. [Allow both delete and add to the system]
\end{enumerate}

\subsection{Encoding edge addition}
One of the source of incomplete information in the given VTS system is knowledge of all the edges it contain. If this information is missing our tool will suggest a few modification to the given VTS by adding additional edges to fill the missing information that is compatible with the rules of the VTS.

\begin{align}
  \exists n_{i_k} \, a_{i_k} \, e_{i_j_q_k} \, b_{i_j_q_k} \, p_{k_k^{\dash}} \,  r_{i_j} \, 
               ( basic_vts_constraints \land  vts\_activity\_constraint \land  given\_vts\_information \land  restriction\_on\_modification )   
  \tag{E1}\label{eq:addedge1}
\end{align}

The basic_vts_constraints and vts_activity_constraint are same as the previous sections, describing stability of the graph and fusion of the edge into the node and the molecular activity describing the active state of a molecule. The given_vts_information is encoded using a front end input language. The user provides the information of the VTS with a partial information using this front end. Our tool then converts these inputs into the constraints over the given VTS.

We encode the restriction_on_modification by putting the constraints on the unassigned edges and edge labels. The constraint of allowing only certain number of addition to the given VTS is encoded as at_most_k() function over the unassigned edges and label.

\begin{align}
    constraint on edge = atmost\_k\_allowed ( unassigned edges in VTS )

    constraints of the molecular activity on the edge = at\_most\_k ( unassigned activity labels in VTS edges )
    constraints of the molecule presence on the edge = at\_most\_k ( unassigned molecule labels in VTS edges )\label{eq:addedge2}
\end{align}

@@

\begin{align}
 \exists e_{i_j_q} ( connectivity\_constraint && self\_edge\_restriction && \ref{eq:addedge1} )    
  \tag{E1}\label{eq:addedge2}
\end{align}

The connectivity_constraint && self_edge_restriction are same as the previous sections, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS. addedge1 is the constraint of \ref{eq:addedge1}.

@@

    auto addConstraints = edgeC && edgeActivityC && edgePresenceC  && fixVar0;

    auto qvtsCons = exists( setN, 
                    exists( setActiveN, 
                    exists( setPresenceE,  
                    exists( setActiveE, 
                    exists( setPairingM, 
                    exists( setReach, 
                            vtsCons && vtsActivity && inputCons && addConstraints ))))));

>>>>

The missing information can be in any of these combinations parts of VTS. For example existence of some undiscovered edges or nodes, or insufficient knowledge about the presence of molecules in some part of the VTS (either on the node or on the edge). To cover most of the likely variations of this missing information we have encoded the following variants of VTS synthesis.
%
%
\begin{enumerate}[label=\Alph*]
\item  Add new edges to the given VTS to achieve graph stability, fusion and k connected. 
\item  Modify the flow of molecules on the nodes and on the edges.
  \begin{enumerate}
  	\item use available set of molecules.
    \item allow new molecule type to be added.     
  \end{enumerate}        
\item Learning meaningful activity function. 
  \begin{enumerate}
    \item kcnf: low depth circuit.
    \item Boolean gates: And, Or.
    \item Boolean gates with linear combination.  
    \end{enumerate}        
  % - Function dependence with var occurring once.
\item  VTS repair. [Allow both delete and add to the system]
\end{enumerate}

\begin{align}
  \exists n_{i_k} \, a_{i_k} \, e_{ijqk} \, b_{ijqk} \, p_{k_{k^{-}}} \,  r_{i_j} \, 
               ( basic_vts_constraints \land  vts\_activity\_constraint \land  given\_vts\_information \land  restriction\_on\_modification )   
  \tag{E1}\label{eq:addedge1}
\end{align}

The basicvtsconstraints and vtsactivityconstraint are same as the previous sections, describing stability of the graph and fusion of the edge into the node and the molecular activity describing the active state of a molecule. The givenvtsinformation is encoded using a front end input language. The user provides the information of the VTS with a partial information using this front end. Our tool then converts these inputs into the constraints over the given VTS.

We encode the restriction\_on\_modification by putting the constraints on the unassigned edges and edge labels. The constraint of allowing only certain number of addition to the given VTS is encoded as at\_most\_k() function over the unassigned edges and label.

\begin{align}
    constraint on edge = atmost\_k\_allowed ( unassigned edges in VTS )    
    constraints of the molecular activity on the edge = at\_most\_k ( unassigned activity labels in VTS edges )
    constraints of the molecule presence on the edge = at\_most\_k ( unassigned molecule labels in VTS edges )\label{eq:addedge2}
\end{align}

@@

\begin{align}
 \exists e_{ijq} ( connectivity\_constraint && self\_edge\_restriction && \ref{eq:addedge1} )    
  \tag{E1}\label{eq:addedge2}
\end{align}

The connectivity\_constraint \&\& self\_edge\_restriction are same as the previous sections, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS. addedge1 is the constraint of \ref{eq:addedge1}.

@@

    auto addConstraints = edgeC \&\& edgeActivityC \&\& edgePresenceC  \&\& fixVar0;

    auto qvtsCons = exists( setN, 
                    exists( setActiveN, 
                    exists( setPresenceE,  
                    exists( setActiveE, 
                    exists( setPairingM, 
                    exists( setReach, 
                            vtsCons \&\& vtsActivity \&\& inputCons \&\& addConstraints ))))));

### 2018-04-22 papers/synth/intro.tex
fixing start
parsing fixed

Vesicle Traffic Systems(VTS) are the material transport mechanisms
among the compartments inside the biological cells~\cite{vtsIntro}.
%
\ashu{Describe VTS in detail}
%
Vesicle Traffic Systems are the transport mechanisms inside the cells.
%
Different compartments are viewed as nodes and transport channels are
nodes between the graphs.

>>>>

%Motivate VTS
Eukaryotic cells, including human cells, consists of multiple compartments.
%
Vesicle Traffic Systems(VTSs) are the material transport mechanisms
among the compartments inside the eukaryotic cells~\cite{vtsIntro}.
%
Almost all subsystems of eukaryotic cells depend on VTSs.
%
Therefore, understanding how VTSs functions is one of the key
questions of cell biology.
%
In this paper, we are looking at the computational questions 
arise from the VTSs.
%
In the following, we use the model of VTSs that has been presented
in~\cite{VTS}.
%
Please look at appendix~\ref{sec:model}
for the detailed discussion on pros and cons of the model.

% Describe VTS in detail
While molecules are transported by VTSs, VTSs are also
regulated by the molecules.
%
Each compartment contains a set of molecules.
%
The molecules are transported to the other compartments via
unidirectional channels.  
%
The molecules in a compartment may be active or not active.
%
Similarly, a molecule can be active along in a channel. 
%
The active molecules are the regulators of the channels.
%
A channel is enabled by a pair of molecules
such that one occurs in the channel and the other
occurs in the destination compartment.
%
Both the molecules must be active in the channel
and compartment respectively.
%
The pairs are called {\em fusing} molecules and analogously
the channel is considered to be {\em fused} with the
compartment.
%
Not all the pairs of molecules can participate in the fusion, it is
usually determined by wet experiments the potential fusion pairs.
%
To ensure effective regulation, the fusing molecule pairs must be
unique for each fused channel-compartment pair.
%
Since a molecule has to be active in order to participate in fusion,
the molecule may be present in the other places without being active
and does not interfere with regulation of the other fused
channel-compartment pairs.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecule in a compartment or
channel may make the active or inactive.
%
We call this regulation {\em activity functions}.

Although the VTSs are very important, our understanding

In the VTS model, we assume that the system is in study state and
the concentration of molecules does not change over time.
%
Therefore, there is no aspect of

%
They are known

Some of the molecules that are pre
%
%
Different compartments are viewed as nodes and transport channels are
nodes between the graphs.

### 2018-04-22 papers/synth/model.tex
parsing fixed

In this section we will present a list of problems that may arise from
synthesis of VTSs from partial available information.

\subsection{Problem Statements}

Our objective is to find missing parts of a partially known VTSs.
%
We will consider several variations of the problem.
%
\begin{itemize}
\item Learning activity functions
\item Modifying labels of the nodes and edges
\item Adding missing edges
\item Adding
\end{itemize}

%Types of questions we are trying to solve.

The missing information can be in any of these combinations parts of VTS. For example existence of some undiscovered edges or nodes, or insufficient knowledge about the presence of molecules in some part of the VTS (either on the node or on the edge). To cover most of the likely variations of this missing information we have encoded the following variants of VTS synthesis.
%
%
\begin{enumerate}[label=\Alph*]
\item  Add new edges to the given VTS to achieve graph stability, fusion and k connected. 
\item  Modify the flow of molecules on the nodes and on the edges.
  \begin{enumerate}
  	\item use available set of molecules.
    \item allow new molecule type to be added.     
  \end{enumerate}        
\item Learning meaningful activity function. 
  \begin{enumerate}
    \item kcnf: low depth circuit.
    \item Boolean gates: And, Or.
    \item Boolean gates with linear combination.  
    \end{enumerate}        
  % - Function dependence with var occurring once.
\item  VTS repair. [Allow both delete and add to the system]
\end{enumerate}

\begin{align}
  \exists n_{i_k} \, a_{i_k} \, e_{ijqk} \, b_{ijqk} \, p_{k_{k^{-}}} \,  r_{i_j} \, 
               ( basic_vts_constraints \land  vts\_activity\_constraint \land  given\_vts\_information \land  restriction\_on\_modification )   
  \tag{E1}\label{eq:addedge1}
\end{align}

The basicvtsconstraints and vtsactivityconstraint are same as the previous sections, describing stability of the graph and fusion of the edge into the node and the molecular activity describing the active state of a molecule. The givenvtsinformation is encoded using a front end input language. The user provides the information of the VTS with a partial information using this front end. Our tool then converts these inputs into the constraints over the given VTS.

We encode the restriction\_on\_modification by putting the constraints on the unassigned edges and edge labels. The constraint of allowing only certain number of addition to the given VTS is encoded as at\_most\_k() function over the unassigned edges and label.

\begin{align}
    constraint on edge = atmost\_k\_allowed ( unassigned edges in VTS )    
    constraints of the molecular activity on the edge = at\_most\_k ( unassigned activity labels in VTS edges )
    constraints of the molecule presence on the edge = at\_most\_k ( unassigned molecule labels in VTS edges )\label{eq:addedge2}
\end{align}

Put \ref{eq:addedge2} in symbolic form and explain it in a couple of lines.

In order to decrease the search space we do not allow any modification in the node label and activity on the nodes. This constraint can be encoded as the fixing all the unassigned bits to false.

%    // Fix rest of them to zero.
%    auto fixVar0 = ! z3::mk_or ( openN )  && ! z3::mk_or ( openActiveN );

\begin{align}
 \exists e_{ijq} ( connectivity\_constraint && self\_edge\_restriction && \ref{eq:addedge1} )    
  \tag{E1}\label{eq:addedge2}
\end{align}

The connectivity\_constraint \&\& self\_edge\_restriction are same as the previous sections, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS. addedge1 is the constraint of \ref{eq:addedge1}.

%{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )

    auto addConstraints = edgeC \&\& edgeActivityC \&\& edgePresenceC  \&\& fixVar0;

    auto qvtsCons = exists( setN, 
                    exists( setActiveN, 
                    exists( setPresenceE,  
                    exists( setActiveE, 
                    exists( setPairingM, 
                    exists( setReach, 
                            vtsCons \&\& vtsActivity \&\& inputCons \&\& addConstraints ))))));

\subsection{Encoding molecules presence}

\subsection{Encoding low depth cnf circuits}

\subsection{Encoding boolean gates}

\subsection{Encoding vts repair}
The repair of the VTS requires both the addition and the deletion of the present molecules, node molecules pairing matrix and activity of the molecules. We have encoded the vts repair in our tool using the dummy xor bits.

\subsection{QBF encodings}

>>>>

\ashu{Discuss the model in Biological terms.}
